Transform and Tell:\\The News Image Caption Writer That Remembers Rare Names

### 2019-11-13 paper/section_3_model.tex
Work on attention section

Given an input of length $S$, the pretrained RoBERTa encoder will return 25
sequences of embeddings, $\bm{h}_i \in \mathbb{R}^{2048 \times S}$ for $i \in
\{0,1, 2,...,24\}$. This includes the initial uncontextualized embeddings and
the output of each of the 24 layers. Inspired by Tenney \etal
\cite{Tenney2019BertRT}, who showed that different layers in BERT represent
different steps in the traditional NLP pipeline, we take a weighted sum
across all layers to obtain the article embedding:
\begin{IEEEeqnarray*}{lCl}
   \bx_T &=& \sum_{i=0}^{24} w_i \bm{h}_i
\end{IEEEeqnarray*}
where $\bx_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
and $w_i$ are learnable weights.

@@

The decoder is a function that estimates $p(y_t)$, the probability of the next
token, conditional on the past and the context embeddings $\bx_I$, $\bx_T$, and
$\bx_F$:
\begin{IEEEeqnarray*}{lCl}
   p(y_t) &=& \mathbb{P}(Y_t = y_t | y_{<t}, \bx_I, \bx_T, \bx_F)
\end{IEEEeqnarray*}

@@

In the standard self-attention module, the input embedding $\bx \in
\mathbb{R}^{1024}$ is first projected linearly into a query, key, and value
$\bm{q}, \bm{k}, \bm{v} \in \mathbb{R}^{1024}$. Then the attention is the
weighted sum of the values, where the weights are obtained from the dot product
between the key and value:
\begin{IEEEeqnarray*}{lCl}
   \text{Attention}(\bx) &=&
   \text{softmax}\left( \dfrac{\bm{q} \bm{k}^T}{\sqrt{d_K}} \right) \bm{v}
\end{IEEEeqnarray*}

\subsubsection{Encoder Attention}

>>>>

Given an input of length $S$, the pretrained RoBERTa encoder will return 25
sequences of embeddings, $\bg_i \in \mathbb{R}^{2048 \times S}$ for $i \in
\{0,1, 2,...,24\}$. This includes the initial uncontextualized embeddings and
the output of each of the 24 layers. Inspired by Tenney \etal
\cite{Tenney2019BertRT}, who showed that different layers in BERT represent
different steps in the traditional NLP pipeline, we take a weighted sum
across all layers to obtain the article embedding:
\begin{IEEEeqnarray*}{lCl}
   \bx_T &=& \sum_{i=0}^{24} \alpha_i \bg_i
\end{IEEEeqnarray*}
where $\bx_T \in \mathbb{R}^{1024 \times S}$ is the article embedding
and $\alpha_i$ are learnable weights.

@@

The decoder is a function that estimates $p(y_t)$, the probability of the next
token, conditional on the past and the context embeddings $\bx_I$, $\bx_T$, and
$\bx_F$:
\begin{IEEEeqnarray*}{lCl}
   p(y_t) &=& \mathbb{P}(Y_t = y_t \mid \by_{<t}, \bx_I, \bx_T, \bx_F)
\end{IEEEeqnarray*}
In our architecture, the decoder consists of four layers of transformer blocks.
In each block, the conditioning on past tokens is computed using dynamic
convolutions \cite{Wu2018PayLA}, and the conditioning on the contexts is
computed using Scalar-Dot-Product attention \cite{Vaswani2017AttentionIA}.

\subsubsection{Scalar-Dot-Product Attention}

Let $\bh_t$ be the current hidden state. We first do a linear projection of
$\bh_t$ and the image embedding $\bx_I$ into a query, key, and value, so that
all three have the same dimension:
\begin{IEEEeqnarray*}{lCl}
   \bq_T &=& W_{Iq} \, \bh_t \\
   \bk_T &=& W_{Ik} \, \bx_I \\
   \bv_T &=& W_{Iv} \, \bx_I
\end{IEEEeqnarray*}
Then the attended image $\bx_I'$ is the weighted sum of the values, where the weights are
obtained from the dot product between the key and value:
\begin{IEEEeqnarray*}{lCl}
   \bx_I' &=& \text{softmax}\left( \bq \bk^T \right) \bv
\end{IEEEeqnarray*}
We use the same attention mechanism to obtain the attended article $\bx_T'$
and the attended face $\bx_F'$. These three are then concatenated and fed
through a feedforward layer:
\begin{IEEEeqnarray*}{lCl}
   \bx_C' &=& [\bx_I', \bx_T', \bx_F'] \\
   \bx_O &=& \text{LayerNorm}(X_C + W_O \, \text{ReLU}(W_C \, \bx_C' + \bb_C) + \bb_O)
\end{IEEEeqnarray*}

@@

In the standard self-attention module, the input embedding $\bx \in
\mathbb{R}^{1024}$ is first projected linearly into a query, key, and value
$\bm{q}, \bm{k}, \bm{v} \in \mathbb{R}^{1024}$.
